cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-04 paper-cardinalR.Rmd
Updated mathematical notations

```{r branch, eval=knitr::is_html_output(), fig.cap="Viewing the $4\\text{-}D$ output of the `gen_orgcurvybranches()`. The tour view shows how the linear branches appear from multiple viewing angles.", fig.alt="Interactive langevitour of the orglinearbranches dataset in 4-D, showing linear branches from multiple viewing angles.", fig.pos="!ht", layout="l-body"}

@@

```{r branch-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from the $4\\text{-}D$ `orglinearbranches` data. Each shows a different projection, illustrating how the linear branches appear from multiple viewing angles. These views highlight the dataset’s underlying branching structure and demonstrate how projections reveal patterns that are otherwise hidden in higher dimensions.", fig.width=12, fig.height=4, fig.pos="H", fig.alt="Three 2-D projections of the 4-D orglinearbranches dataset, showing different angles of the linear branches to illustrate the branching structure.", fig.pos="!ht"}

@@

```{r cone-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from the $3\\text{-}D$ `cone` data. Points are concentrated near the tip along the height dimension, while the radius of the hyperspherical cross-section decreases linearly toward the apex. These projections show how the conical geometry is preserved.", fig.pos="H", fig.alt="Three 2-D projections of the 3-D cone dataset, showing points concentrated near the tip and the linear decrease in radius toward the apex.", fig.pos="!ht", fig.width=12, fig.height=4}

@@

```{r pyr, eval=knitr::is_html_output(), fig.cap="Viewing the $4\\text{-}D$  `pyrrect`, `pyrtri`, `pyrstar`, and `pyrholes` data. The `pyrrrect` structure forms a dense rectangular base tapering to a narrow tip, while `pytri` shows a more triangular spread with sharper edges. `Pyrstar` extends into multiple pointed branches radiating from a common core, and `pyrholes` reveals hollow or open regions within an otherwise compact shape.", fig.alt="Interactive langevitour of four 4-D pyramid-like datasets: pyrrect, pyrtri, pyrstar, and pyrholes, showing dense bases, triangular spreads, branching points, and hollow regions.", fig.pos="!ht"}

@@

```{r pyr-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data. The `pyrrrect` structure forms a dense rectangular base tapering to a narrow tip, while `pytri` shows a more triangular spread with sharper edges. `Pyrstar` extends into multiple pointed branches radiating from a common core, and `pyrholes` reveals hollow or open regions within an otherwise compact shape. These projections illustrate a range of pyramid-like geometries that vary in density and structure.", fig.width=12, fig.height=16, fig.pos="H", out.width="80%", fig.align='center', fig.alt="Three 2-D projections from each of four 4-D pyramid-like datasets: pyrrect, pyrtri, pyrstar, and pyrholes, showing their distinct geometries, branching, and hollow regions.", fig.pos="!ht"}

@@

```{r sphere, eval=knitr::is_html_output(), fig.cap="Viewing the $4\\text{-}D$ `circle`, `curvycycle` data, and $3\\text{-}D$ `clusteredspheres` data. The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\\text{-}D$ projections, highlighting how projection can distort spatial relationships.", fig.alt="Interactive langevitour of three datasets: circle and curvycycle in 4-D showing closed-loop and wavy twisted-ring structures, and clusteredspheres in 3-D showing multiple compact spherical clusters with slight overlap in projections.", fig.pos="!ht", layout="l-body"}

@@

```{r sphere-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, `circle` (a1-a3), `curvycycle` (b1-b3), and, $3\\text{-}D$ `clusteredspheres` (c1-c3). The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\\text{-}D$ projections, highlighting how projection can distort spatial relationships. These projections show how simple cyclic, wavy curvilinear, and clustered structures appear in $2\\text{-}D$, emphasizing the effects of projection on density, continuity, and separation", fig.width=12, fig.height=12, out.width="80%", fig.align='center', fig.pos="H", fig.alt="Three 2-D projections from each of three datasets: circle, curvycycle, and clusteredspheres, showing closed loops, twisted rings, and compact spherical clusters, illustrating projection effects on structure, density, and separation.", fig.pos="!ht"}

@@

```{r trefoil, eval=knitr::is_html_output(), fig.cap="Viewing the $4\\text{-}D$ `trefoil4d` and $3\\text{-}D$ `trefoil3d` data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space.", fig.alt="Interactive langevitour of two trefoil knot datasets: trefoil4d in 4-D showing complex twisting and looping patterns, and trefoil3d in 3-D showing a simpler compact knot-like form.", fig.pos="!ht"}

@@

```{r trefoil-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, `trefoil4d` (a1-a3) and $3\\text{-}D$ `trefoil3d` (b1-b3) data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space. These projections illustrate a range of looping structures in high-dimensions.", fig.width=12, fig.height=8, fig.pos="H", out.width="80%", fig.align='center', fig.alt="Three 2-D projections from each of two trefoil knot datasets, showing complex 4-D trefoil loops and simpler 3-D knot structures, illustrating curvature, twisting, and separation across dimensions.", fig.pos="!ht"}

@@

```{r triginometric, eval=knitr::is_html_output(), fig.cap="Viewing the $4\\text{-}D$ `crescent`, `curvycylinder`, `sphericalspiral`, `helicalspiral`, `conicspiral`, and `nonlinear` data. The `curvycylinder` shows a cylindrical manifold with a nonlinear twist along its height, producing smooth, continuous curvature. The `sphericalspiral` forms a spiral path on a spherical surface, combining circular and vertical motion in a helical form. The `conicspiral` spreads radially while ascending, forming a conical helix with twisting variations in a non-radial dimension. The `nonlinear` dataset exhibits a warped $2\\text{-}D$ surface with sharp oscillations and smooth waves, reflecting complex nonlinear interactions.", fig.alt="Interactive langevitour of six datasets in 4-D: crescent, curvycylinder, sphericalspiral, helicalspiral, conicspiral, and nonlinear, showing cylindrical twists, spiral paths, conical helices, and warped 2-D surfaces with smooth and sharp variations.", fig.pos="!ht"}

@@

```{r triginometric-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvycylinder` (a1-a3), `sphericalspiral` (b1-b3), `conicspiral` (c1-c3), and `nonlinear` (d1-d3) data. The `curvycylinder` shows a cylindrical manifold with a nonlinear twist along its height, producing smooth, continuous curvature. The `sphericalspiral` forms a spiral path on a spherical surface, combining circular and vertical motion in a helical form. The `conicspiral` spreads radially while ascending, forming a conical helix with twisting variations in a non-radial dimension. The `nonlinear` dataset exhibits a warped $2\\text{-}D$ surface with sharp oscillations and smooth waves, reflecting complex nonlinear interactions. Each shows variations in curvature, density, and continuity.", fig.width=12, fig.height=16, out.width="70%", fig.align='center', fig.pos="H", fig.alt="Three 2-D projections from each of four 4-D datasets: curvycylinder, sphericalspiral, conicspiral, and nonlinear, showing cylindrical twists, spiral and conical helices, and warped 2-D surfaces, illustrating curvature, density, and continuity.", fig.pos="!ht"}

@@

```{r highd-data, eval=knitr::is_html_output(), fig.cap="Viewing five synthetic clusters with distinct geometric structures: a helical spiral, a hemisphere, a uniform cube, a cone, and a Gaussian cluster.", fig.alt="Interactive langevitour of five synthetic clusters in 4-D: helical spiral, hemisphere, uniform cube, cone, and Gaussian cluster, each colored distinctly to highlight geometric structure.", fig.pos="!ht"}

@@

```{r highd-proj, eval=knitr::is_latex_output(), fig.pos="!ht", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green.", fig.alt="Three 2-D projections of five 4-D synthetic clusters: helical spiral (dark green), hemisphere (orange), uniform cube (purple), cone (pink), and Gaussian (light green), showing spatial separation and cluster geometry.", fig.width=12, fig.height=4, fig.pos="!ht"}

>>>>

```{r branch, eval=knitr::is_html_output(), fig.cap="Viewing the $4\\text{-}D$ output of the `gen_orgcurvybranches()`. The tour view shows how the linear branches appear from multiple viewing angles.", fig.alt="Interactive langevitour of the orglinearbranches dataset in $4\\text{-}D$, showing linear branches from multiple viewing angles.", fig.pos="!ht", layout="l-body"}

@@

```{r branch-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from the $4\\text{-}D$ `orglinearbranches` data. Each shows a different projection, illustrating how the linear branches appear from multiple viewing angles. These views highlight the dataset’s underlying branching structure and demonstrate how projections reveal patterns that are otherwise hidden in higher dimensions.", fig.width=12, fig.height=4, fig.pos="H", fig.alt="Three $2\\text{-}D$ projections of the $4\\text{-}D$ orglinearbranches dataset, showing different angles of the linear branches to illustrate the branching structure.", fig.pos="!ht"}

@@

```{r cone-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from the $3\\text{-}D$ `cone` data. Points are concentrated near the tip along the height dimension, while the radius of the hyperspherical cross-section decreases linearly toward the apex. These projections show how the conical geometry is preserved.", fig.pos="H", fig.alt="Three $2\\text{-}D$ projections of the 3-D cone dataset, showing points concentrated near the tip and the linear decrease in radius toward the apex.", fig.pos="!ht", fig.width=12, fig.height=4}

@@

```{r pyr, eval=knitr::is_html_output(), fig.cap="Viewing the $4\\text{-}D$  `pyrrect`, `pyrtri`, `pyrstar`, and `pyrholes` data. The `pyrrrect` structure forms a dense rectangular base tapering to a narrow tip, while `pytri` shows a more triangular spread with sharper edges. `Pyrstar` extends into multiple pointed branches radiating from a common core, and `pyrholes` reveals hollow or open regions within an otherwise compact shape.", fig.alt="Interactive langevitour of four $4\\text{-}D$ pyramid-like datasets: pyrrect, pyrtri, pyrstar, and pyrholes, showing dense bases, triangular spreads, branching points, and hollow regions.", fig.pos="!ht"}

@@

```{r pyr-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data. The `pyrrrect` structure forms a dense rectangular base tapering to a narrow tip, while `pytri` shows a more triangular spread with sharper edges. `Pyrstar` extends into multiple pointed branches radiating from a common core, and `pyrholes` reveals hollow or open regions within an otherwise compact shape. These projections illustrate a range of pyramid-like geometries that vary in density and structure.", fig.width=12, fig.height=16, fig.pos="H", out.width="80%", fig.align='center', fig.alt="Three $2\\text{-}D$ projections from each of four $4\\text{-}D$ pyramid-like datasets: pyrrect, pyrtri, pyrstar, and pyrholes, showing their distinct geometries, branching, and hollow regions.", fig.pos="!ht"}

@@

```{r sphere, eval=knitr::is_html_output(), fig.cap="Viewing the $4\\text{-}D$ `circle`, `curvycycle` data, and $3\\text{-}D$ `clusteredspheres` data. The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\\text{-}D$ projections, highlighting how projection can distort spatial relationships.", fig.alt="Interactive langevitour of three datasets: circle and curvycycle in $4\\text{-}D$ showing closed-loop and wavy twisted-ring structures, and clusteredspheres in 3-D showing multiple compact spherical clusters with slight overlap in projections.", fig.pos="!ht", layout="l-body"}

@@

```{r sphere-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, `circle` (a1-a3), `curvycycle` (b1-b3), and, $3\\text{-}D$ `clusteredspheres` (c1-c3). The `circle` structure forms a smooth, closed loop, while `curvycycle` shows a wavy, continuous pattern forming a twisted ring. The `clusteredspheres` dataset displays multiple compact spherical groups that are clearly separated in higher dimensions but overlap slightly in some $2\\text{-}D$ projections, highlighting how projection can distort spatial relationships. These projections show how simple cyclic, wavy curvilinear, and clustered structures appear in $2\\text{-}D$, emphasizing the effects of projection on density, continuity, and separation", fig.width=12, fig.height=12, out.width="80%", fig.align='center', fig.pos="H", fig.alt="Three $2\\text{-}D$ projections from each of three datasets: circle, curvycycle, and clusteredspheres, showing closed loops, twisted rings, and compact spherical clusters, illustrating projection effects on structure, density, and separation.", fig.pos="!ht"}

@@

```{r trefoil, eval=knitr::is_html_output(), fig.cap="Viewing the $4\\text{-}D$ `trefoil4d` and $3\\text{-}D$ `trefoil3d` data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space.", fig.alt="Interactive langevitour of two trefoil knot datasets: trefoil4d in $4\\text{-}D$ showing complex twisting and looping patterns, and trefoil3d in 3-D showing a simpler compact knot-like form.", fig.pos="!ht"}

@@

```{r trefoil-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, `trefoil4d` (a1-a3) and $3\\text{-}D$ `trefoil3d` (b1-b3) data. The `trefoil4d` structure represents a higher-dimensional extension of the classic trefoil knot, revealing complex twisting and looping patterns that remain continuous across projections. In contrast, the `trefoil3d` dataset maintains a simpler, more compact knot-like form, showing how dimensional extension adds curvature and separation in the embedded space. These projections illustrate a range of looping structures in high-dimensions.", fig.width=12, fig.height=8, fig.pos="H", out.width="80%", fig.align='center', fig.alt="Three $2\\text{-}D$ projections from each of two trefoil knot datasets, showing complex $4\\text{-}D$ trefoil loops and simpler 3-D knot structures, illustrating curvature, twisting, and separation across dimensions.", fig.pos="!ht"}

@@

```{r triginometric, eval=knitr::is_html_output(), fig.cap="Viewing the $4\\text{-}D$ `crescent`, `curvycylinder`, `sphericalspiral`, `helicalspiral`, `conicspiral`, and `nonlinear` data. The `curvycylinder` shows a cylindrical manifold with a nonlinear twist along its height, producing smooth, continuous curvature. The `sphericalspiral` forms a spiral path on a spherical surface, combining circular and vertical motion in a helical form. The `conicspiral` spreads radially while ascending, forming a conical helix with twisting variations in a non-radial dimension. The `nonlinear` dataset exhibits a warped $2\\text{-}D$ surface with sharp oscillations and smooth waves, reflecting complex nonlinear interactions.", fig.alt="Interactive langevitour of six datasets in $4\\text{-}D$: crescent, curvycylinder, sphericalspiral, helicalspiral, conicspiral, and nonlinear, showing cylindrical twists, spiral paths, conical helices, and warped $2\\text{-}D$ surfaces with smooth and sharp variations.", fig.pos="!ht"}

@@

```{r triginometric-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvycylinder` (a1-a3), `sphericalspiral` (b1-b3), `conicspiral` (c1-c3), and `nonlinear` (d1-d3) data. The `curvycylinder` shows a cylindrical manifold with a nonlinear twist along its height, producing smooth, continuous curvature. The `sphericalspiral` forms a spiral path on a spherical surface, combining circular and vertical motion in a helical form. The `conicspiral` spreads radially while ascending, forming a conical helix with twisting variations in a non-radial dimension. The `nonlinear` dataset exhibits a warped $2\\text{-}D$ surface with sharp oscillations and smooth waves, reflecting complex nonlinear interactions. Each shows variations in curvature, density, and continuity.", fig.width=12, fig.height=16, out.width="70%", fig.align='center', fig.pos="H", fig.alt="Three $2\\text{-}D$ projections from each of four $4\\text{-}D$ datasets: curvycylinder, sphericalspiral, conicspiral, and nonlinear, showing cylindrical twists, spiral and conical helices, and warped $2\\text{-}D$ surfaces, illustrating curvature, density, and continuity.", fig.pos="!ht"}

@@

```{r highd-data, eval=knitr::is_html_output(), fig.cap="Viewing five synthetic clusters with distinct geometric structures: a helical spiral, a hemisphere, a uniform cube, a cone, and a Gaussian cluster.", fig.alt="Interactive langevitour of five synthetic clusters in $4\\text{-}D$: helical spiral, hemisphere, uniform cube, cone, and Gaussian cluster, each colored distinctly to highlight geometric structure.", fig.pos="!ht"}

@@

```{r highd-proj, eval=knitr::is_latex_output(), fig.pos="!ht", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green.", fig.alt="Three $2\\text{-}D$ projections of five $4\\text{-}D$ synthetic clusters: helical spiral (dark green), hemisphere (orange), uniform cube (purple), cone (pink), and Gaussian (light green), showing spatial separation and cluster geometry.", fig.width=12, fig.height=4, fig.pos="!ht"}

### 2025-12-04 paper-cardinalR.tex
Updated mathematical notations

\begin{figure}[!ht]
\includegraphics[width=1\linewidth,alt={Three 2-D projections of the 4-D orglinearbranches dataset, showing different angles of the linear branches to illustrate the branching structure.}]{paper-cardinalR_files/figure-latex/branch-proj-1} \caption{Three $2\text{-}D$ projections from the $4\text{-}D$ `orglinearbranches` data. Each shows a different projection, illustrating how the linear branches appear from multiple viewing angles. These views highlight the dataset’s underlying branching structure and demonstrate how projections reveal patterns that are otherwise hidden in higher dimensions.}\label{fig:branch-proj}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=1\linewidth,alt={Three 2-D projections of the 3-D cone dataset, showing points concentrated near the tip and the linear decrease in radius toward the apex.}]{paper-cardinalR_files/figure-latex/cone-proj-1} \caption{Three $2\text{-}D$ projections from the $3\text{-}D$ `cone` data. Points are concentrated near the tip along the height dimension, while the radius of the hyperspherical cross-section decreases linearly toward the apex. These projections show how the conical geometry is preserved.}\label{fig:cone-proj}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth,alt={Three 2-D projections from each of four 4-D pyramid-like datasets: pyrrect, pyrtri, pyrstar, and pyrholes, showing their distinct geometries, branching, and hollow regions.}]{paper-cardinalR_files/figure-latex/pyr-proj-1}

@@

{\centering \includegraphics[width=0.8\linewidth,alt={Three 2-D projections from each of three datasets: circle, curvycycle, and clusteredspheres, showing closed loops, twisted rings, and compact spherical clusters, illustrating projection effects on structure, density, and separation.}]{paper-cardinalR_files/figure-latex/sphere-proj-1}

@@

{\centering \includegraphics[width=0.8\linewidth,alt={Three 2-D projections from each of two trefoil knot datasets, showing complex 4-D trefoil loops and simpler 3-D knot structures, illustrating curvature, twisting, and separation across dimensions.}]{paper-cardinalR_files/figure-latex/trefoil-proj-1}

@@

{\centering \includegraphics[width=0.7\linewidth,alt={Three 2-D projections from each of four 4-D datasets: curvycylinder, sphericalspiral, conicspiral, and nonlinear, showing cylindrical twists, spiral and conical helices, and warped 2-D surfaces, illustrating curvature, density, and continuity.}]{paper-cardinalR_files/figure-latex/triginometric-proj-1}

@@

\begin{figure}[!ht]
\includegraphics[width=1\linewidth,alt={Three 2-D projections of five 4-D synthetic clusters: helical spiral (dark green), hemisphere (orange), uniform cube (purple), cone (pink), and Gaussian (light green), showing spatial separation and cluster geometry.}]{paper-cardinalR_files/figure-latex/highd-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green.}\label{fig:highd-proj}
\end{figure}

>>>>

\begin{figure}[!ht]
\includegraphics[width=1\linewidth,alt={Three $2\text{-}D$ projections of the $4\text{-}D$ orglinearbranches dataset, showing different angles of the linear branches to illustrate the branching structure.}]{paper-cardinalR_files/figure-latex/branch-proj-1} \caption{Three $2\text{-}D$ projections from the $4\text{-}D$ `orglinearbranches` data. Each shows a different projection, illustrating how the linear branches appear from multiple viewing angles. These views highlight the dataset’s underlying branching structure and demonstrate how projections reveal patterns that are otherwise hidden in higher dimensions.}\label{fig:branch-proj}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=1\linewidth,alt={Three $2\text{-}D$ projections of the 3-D cone dataset, showing points concentrated near the tip and the linear decrease in radius toward the apex.}]{paper-cardinalR_files/figure-latex/cone-proj-1} \caption{Three $2\text{-}D$ projections from the $3\text{-}D$ `cone` data. Points are concentrated near the tip along the height dimension, while the radius of the hyperspherical cross-section decreases linearly toward the apex. These projections show how the conical geometry is preserved.}\label{fig:cone-proj}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth,alt={Three $2\text{-}D$ projections from each of four $4\text{-}D$ pyramid-like datasets: pyrrect, pyrtri, pyrstar, and pyrholes, showing their distinct geometries, branching, and hollow regions.}]{paper-cardinalR_files/figure-latex/pyr-proj-1}

@@

{\centering \includegraphics[width=0.8\linewidth,alt={Three $2\text{-}D$ projections from each of three datasets: circle, curvycycle, and clusteredspheres, showing closed loops, twisted rings, and compact spherical clusters, illustrating projection effects on structure, density, and separation.}]{paper-cardinalR_files/figure-latex/sphere-proj-1}

@@

{\centering \includegraphics[width=0.8\linewidth,alt={Three $2\text{-}D$ projections from each of two trefoil knot datasets, showing complex $4\text{-}D$ trefoil loops and simpler 3-D knot structures, illustrating curvature, twisting, and separation across dimensions.}]{paper-cardinalR_files/figure-latex/trefoil-proj-1}

@@

{\centering \includegraphics[width=0.7\linewidth,alt={Three $2\text{-}D$ projections from each of four $4\text{-}D$ datasets: curvycylinder, sphericalspiral, conicspiral, and nonlinear, showing cylindrical twists, spiral and conical helices, and warped $2\text{-}D$ surfaces, illustrating curvature, density, and continuity.}]{paper-cardinalR_files/figure-latex/triginometric-proj-1}

@@

\begin{figure}[!ht]
\includegraphics[width=1\linewidth,alt={Three $2\text{-}D$ projections of five $4\text{-}D$ synthetic clusters: helical spiral (dark green), hemisphere (orange), uniform cube (purple), cone (pink), and Gaussian (light green), showing spatial separation and cluster geometry.}]{paper-cardinalR_files/figure-latex/highd-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green.}\label{fig:highd-proj}
\end{figure}
